Rapid and Accurate Global PTM Discovery (G-PTM-D) Using Post-Acquisition Spectral Calibration and Multi-Notch Searches

### 2017-07-13 paper.tex
calib

Calibration quality improvements are further shown through the results of a standard 10ppm precursor tolerance database search (Table~\ref{tbl:calib}).
PSMs within 1\% FDR prior to calibration are compared with PSMs after the calibration procedure (Table~\ref{tbl:calib}).
The calibration procedure successfully addresses instrument miscalibration by centering the average error around zero.
The systemic noise introduced by various other factors is also addressed: this is evident in the decrease in the standard deviation of the errors in the precursor mass estimates, which show that the calibrated mass spectra have sub-ppm mass errors.
Histograms of the mass errors in identified peptides before and after calibration are plotted in Figure~\ref{fgr:fig2-10ppmSearchCalib}.
The main results of calibration in summary are increased PSMs at 1\% FDR, decreased error in precursor mass, and decreased standard deviation in average mass error.

\begin{table}[]
\centering
\caption{PSMs Within 1\% FDR Before and After Calibration}
\label{tbl:calib}
\begin{tabular}{llll}

                                                                                &      & Orig        & Calib        \\
 &PSM Count                                                           &      217612   &   219172        \\
 &Average Error (ppm)                                                              &      -2.10      &        -0.16      \\
 &St. Dev of Error                                                    &       2.15      &        0.91      \\
Confidence Intervals& 68.3\%     &    [-4.26,0.05]          &  [-1.08,0.75]            \\
                                                                                & 95.4\%      &   [-6.41,2.20]          &      [-1.99,1.61]         \\
                                                                                & 99.7\%       &    [-8.56,4.36]          &      [-2.90,2.58]         \\
\end{tabular}
\end{table}

\begin{figure}[H]
 \includegraphics{fig2-10ppmSearchCalib.png}
 \caption{Errors in m/z plotted vs the m/z value and the retention time}
 \label{fgr:fig2-10ppmSearchCalib}
\end{figure}

>>>>

Calibration quality improvements are further shown through the results of standard 10ppm precursor tolerance database search, conducted on uncalibrated vs calibrated spectra files.
Table~\ref{tbl:calib} details the results of these searches, showing the number of confidently identified PSMs, the average ppm differences between the identified peptide and the precursor mass, and the standard deviation of those differences.
The calibration procedure successfully addresses instrument miscalibration by centering the average ppm error around zero.
The systemic noise introduced by various other factors is also addressed: this is evident in the decrease in the standard deviation of the errors in the precursor mass estimates, which show that the calibrated mass spectra have sub-ppm mass errors.
Histograms of the mass errors in identified peptides before and after calibration are plotted in Figure~\ref{fgr:fig2-10ppmSearchCalib}.
The main results of calibration in summary are increased PSMs at 1\% FDR, decreased error in precursor mass, and decreased standard deviation in average mass error.

\begin{table}[]
\centering
\caption{PSMs Within 1\% FDR Before and After Calibration}
\label{tbl:calib}
\begin{tabular}{lll}

                                                                                      & Orig        & Calib        \\
 PSM Count                                                           &      217612   &   219172        \\
 Average Error (ppm)                                                              &      -2.10      &        -0.16      \\
 St. Dev of Error                                                    &       2.15      &        0.91      \\
\end{tabular}
\end{table}

\begin{figure}[H]
 \includegraphics{fig2-10ppmSearchCalib.png}
 \caption{Histograms of the mass errors in identified peptides before and after calibration}
 \label{fgr:fig2-10ppmSearchCalib}
\end{figure}
